---
output: github_document
---

[![Travis build status](https://travis-ci.org/avalcarcel9/GoT.svg?branch=master)](https://travis-ci.org/avalcarcel9/GoT)

[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/avalcarcel9/GoT?branch=master&svg=true)](https://ci.appveyor.com/project/avalcarcel9/GoT)

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/GoT)](https://cran.r-project.org/package=GoT)

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# GoT

The goal of GoT is to help scraping some Game of Thrones data from the internet.

## Installation

You can install the development version from [GitHub](https://github.com/avalcarcel9/GoT) with:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("avalcarcel9/GoT")
```

__Warning: This package scrapes data from the internet. Please be mindful of pinging servers too frequently and of the user agreements for sharing data.__

## Setup

This package is dependent on the `geniusr` package and you must have an API token. Go [here](https://genius.com/) to create an account or login and obtain an API token. For more information on the API creation you can look at the genius documentation [here](https://docs.genius.com/#!#%2Fgetting-started-h1).

Once you’ve created an account and obtained an API they’ll assign you a token. Be sure to copy the token. With the token copied you can add it to the R environment with some code.

Running the following code will open your .Renviron

```{r, eval = FALSE}
user_renviron = path.expand(file.path("~", ".Renviron"))
if(!file.exists(user_renviron)) # check to see if the file already exists
  file.create(user_renviron)
file.edit(user_renviron) # open with another text editor if this fails
```

Once this file is open paste the following into the script:

```{r, eval = FALSE}
GENIUS_API_TOKEN="your-token-goes-here"
```

If done properly then this code will return your API token.

```{r, eval = FALSE}
Sys.getenv("GENIUS_API_TOKEN")
```

## Use

For a more thorough walkthrough please see my [blog post](http://www.alessandravalcarcel.com/blog/2018-04-1-r-rmarkdown-got-scrape/).

```{r}
library(GoT)
```

This package helps you scrape a the Game of Thrones scripts from [www.genius.com](www.genius.com) and some character lists online. 

To scrape the scripts from genius you can use `GoT::scrape_GoT()`.

```{r}
base_url = "https://genius.com/albums/Game-of-thrones"
info = GoT::scrape_GoT(base_url = base_url, season = 7)
head(info)
tail(info)
```

This function will scrape all the seasons up to the season indicated as the function input.

To clean this data somewhat, we can utilize `GoT::cleanGoT()`. This function generally tries to identify the speaking character and removes some of the stage direction or narration.

```{r}
cleaned_data = GoT::cleanGoT(info)
head(cleaned_data)
```

We can also scrape character lists from two websites:

1. [http://awoiaf.westeros.org/index.php/List_of_characters](http://awoiaf.westeros.org/index.php/List_of_characters)
2. [https://www.hbo.com/game-of-thrones/cast-and-crew](https://www.hbo.com/game-of-thrones/cast-and-crew)

```{r}
# Scrape wiki characters and save
url = "http://awoiaf.westeros.org/index.php/List_of_characters"
wiki_characters = GoT::scrape_characters(url)

head(wiki_characters)

# Scrape HBO characters and save
url = 'https://www.hbo.com/game-of-thrones/cast-and-crew'
hbo_characters = GoT::scrape_HBO_characters(url)

head(hbo_characters)
```

## Death Timeline

We can also obtain death timeline data from [https://deathtimeline.com/](https://deathtimeline.com/). 

```{r}
death_times = GoT::get_death_times()
head(death_times)
```

Unfortunately, this timeline only goes up to season 6 so I'll use a this article [http://time.com/3924852/every-game-of-thrones-death/](http://time.com/3924852/every-game-of-thrones-death/) as a supplement. 

```{r}
url = 'http://time.com/3924852/every-game-of-thrones-death/'
time.com_deaths = GoT::get_time.com_deaths(url = url)
head(time.com_deaths)
```




